---
title: "Mapping China and its provinces, municipalities and autonomous regions"
author: "Zhenxing Cheng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mapping China and its provinces, municipalities and autonomous regions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

You can install this package from `github`: 

```{r eval=FALSE, include=TRUE}
devtools::install_github('czxa/hchinamap')
# or use git
devtools::install_git("https://github.com/czxa/hchinamap.git")
```

## Usage

### Mapping China: 

```{r echo=TRUE}
library(dplyr)
library(magrittr)
library(hchinamap)
china <- hchinamap::chinadf %>% 
  dplyr::filter(region == "中国")
hchinamap(name = china$name, value = china$value,
           width = "100%", height = "400px",
           title = "中国地图", region = "中国")
```

Modify the maximum and minimum colors: 

```{r echo=TRUE}
china <- chinadf %>%
  dplyr::filter(region == "中国")
hchinamap(name = china$name, value = china$value,
           width = "100%", height = "400px",
           title = "中国地图",
           minColor = "#f1eef6",
           maxColor = "#980043")
```

## Mapping provinces

For example, map of Anhui

```{r echo=TRUE}
anhui <- chinadf %>%
  dplyr::filter(region == "安徽")
hchinamap(name = anhui$name, value = anhui$value,
           width = "100%", height = "500px",
           title = "Map of Anhui", region = "安徽")
```

Map of Guangdong：

```{r echo=TRUE}
gd <- chinadf %>%
  dplyr::filter(region == "广东")
hchinamap(name = gd$name, value = gd$value,
           width = "100%", height = "400px",
           title = "Map of Guangdong", region = "广东")
```

Map of Heilongjiang：

```{r echo=TRUE}
hlj <- chinadf %>%
  dplyr::filter(region == "黑龙江")
hchinamap(name = hlj$name, value = hlj$value,
           width = "100%", height = "400px",
           title = "黑龙江地图", region = "黑龙江")
```

## Theme

If there are multiple map charts created by this package in a RMarkdown document, use topic parameters carefully, because the charts may interfere with each other.

```{r echo=TRUE}
sx <- chinadf %>%
  dplyr::filter(region == "陕西")
hchinamap(name = sx$name, value = sx$value,
           width = "100%", height = "400px",
           title = "Map of Shaanxi", region = "陕西",
           theme = "darkunica",
           titleColor = "white")
```


## Use it in 'RMarkdown' and 'Shiny' Apps

Here if a very simple 'shiny' example:

```{r eval=FALSE, include=TRUE}
dir <- system.file("examples", "hchinamap", package = "hchinamap")
setwd(dir)
shiny::shinyAppDir(".")
```
