---
title: "Create Maps of China and Maps of Chinese Provinces, Municipalities and Autonomous Regions"
author: "Zhenxing Cheng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Create Maps of China and Maps of Chinese Provinces, Municipalities and Autonomous Regions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

You can install this package from `CRAN` or `GitHub`: 

```{r eval=FALSE, include=TRUE}
# From CRAN
install.packages('hchinamap')

# From  GitHub
devtools::install_github('czxa/hchinamap', build_vignettes = TRUE)
# or use git
devtools::install_git("https://github.com/czxa/hchinamap.git", build_vignettes = TRUE)
```

## Usage

I made a demo datasets for this package. You can load it by following method:

```{r}
dir <- tempdir()
download.file('https://czxb.github.io/br/chinadf.rda', file.path(dir, 'chinadf.rda'))
load(file.path(dir, 'chinadf.rda'), verbose = TRUE)
```

## Additional annotations to parameters

+ region parameter indicate which map to use, you can choose like "China", "Anhui", ... "Macao" and so on. Because the map data of Taiwan have not been collated yet, it is impossible to draw provincial map of Taiwan Province for the time being.
+ name parameter should be in Chinese. like c("北京", "天津", "上海").

### Chinese map:

```{r echo=TRUE}
library(dplyr)
library(magrittr)
library(hchinamap)
china <- chinadf %>% 
  dplyr::filter(region == "China")
hchinamap(name = china$name, value = china$value,
           width = "100%", height = "400px",
          region = "China")
```

Modify the maximum and minimum colors: 

```{r echo=TRUE}
china <- chinadf %>%
  dplyr::filter(region == "China")
hchinamap(name = china$name, value = china$value,
          region = "China",
           width = "100%", height = "400px",
           minColor = "#f1eef6",
           maxColor = "#980043")
```

## Provinces map:

For example, map of Anhui:

```{r echo=TRUE}
anhui <- chinadf %>%
  dplyr::filter(region == "Anhui")
hchinamap(name = anhui$name, value = anhui$value,
           width = "100%", height = "500px",
           title = "Map of Anhui", region = "Anhui")
```

Map of Guangdong：

```{r echo=TRUE}
gd <- chinadf %>%
  dplyr::filter(region == "Guangdong")
hchinamap(name = gd$name, value = gd$value,
           width = "100%", height = "400px",
           title = "Map of Guangdong", region = "Guangdong")
```

Map of Heilongjiang：

```{r echo=TRUE}
hlj <- chinadf %>%
  dplyr::filter(region == "Heilongjiang")
hchinamap(name = hlj$name, value = hlj$value,
           width = "100%", height = "400px",
           title = "Map of Heilongjiang", region = "Heilongjiang")
```

## Theme

If there are multiple map charts created by this package in a RMarkdown document, use topic parameters carefully, because these charts may interfere with each other.

```{r echo=TRUE}
sx <- chinadf %>%
  dplyr::filter(region == "Shaanxi")
hchinamap(name = sx$name, value = sx$value,
           width = "100%", height = "400px",
           title = "Map of Shaanxi", region = "Shaanxi",
           theme = "sandsignika",
           titleColor = "white")
```

## Other parameters

Here is a complete example with all parameters:

```{r}
hchinamap(name = sx$name, value = sx$value,
          width = "100%", height = "400px",
          region = "Shaanxi",
          itermName = "Random data",
          title = "Map of Shaanxi",
          titleAlign = "center",
          titleSize = "20px",
          titleColor = "#333333",
          subtitle = "czxa.top",
          subtitleAlign = 'center',
          subtitleSize = "16px",
          subtitleColor = "#666666",
          min = 0,
          minColor = "rgb(255,255,255)",
          maxColor = "#006cee",
          legendLayout = "horizontal",
          legendAlign = "center",
          legendTitle = "Random Data",
          legendVerticalAlign = "bottom",
          hoverColor = '#a4edba',
          mapNavigation = 0,
          mapNavigationVerticalAlign = "bottom",
          mapNavigationAlign = "left",
          theme = "sunset")
```

## Use it in 'RMarkdown' and 'Shiny' Apps

Here is a very simple 'shiny' example:

```{r eval=FALSE, include=TRUE}
dir <- system.file("examples", "hchinamap", package = "hchinamap")
setwd(dir)
shiny::shinyAppDir(".")
```

------------

<h4 align="center">

License

</h4>

<h6 align="center">

MIT © czxa.top

</h6>
