---
title: "Mark points on Chinese maps and Chinese province maps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mark points on Chinese mps and Chinese province maps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The second function of this package is marking points on Chinese maps and its province maps.

I also made a demo dataset for it, which comes from [Highcharts | Map data center](https://www.highcharts.com.cn/mapdata). To mark points on a map, you need four vector: category, name, latitude, longitude:

```{r}
library(hchinamap)
library(dplyr)
library(magrittr)
dir <- tempdir()
download.file('https://czxb.github.io/br/chinamappointdf.rda', file.path(dir, 'chinamappointdf.rda'))
load(file.path(dir, 'chinamappointdf.rda'), verbose = TRUE)
df <- chinamappointdf
chinamappoint(
	cat = df$cat, name = df$name,
	lat = df$lat, lon = df$lon,
	title = "Urban distribution in China",
	subtitle = "Data source: People's daily",
	width = "100%", height = "500px")
```

If you want to mark points on a province map, you need to use provincepoint() function, which is similar to chinamappoint(), but has one more parameter: region, this parameter is used to specify which province map to use, such as "anhui", "hubei", and so on.

```{r}
df <- chinamappointdf %>% dplyr::filter(province == "Shandong")
provincepoint(cat = df$cat, name = df$name,
    lat = df$lat, lon = df$lon, region = "shandong",
    title = "Urban distribution in Shandong Province",
    subtitle = "Data source: People's daily",
    width = "100%", height = "500px",
    markerRadius = 8)
```

Note: It seems that chinamappoint() and provincepoint() cannot be used in Shiny Applications. I'm working on it!

------------

<h4 align="center">

License

</h4>

<h6 align="center">

MIT © czxa.top

</h6>
